Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-01-07 doc/journal/fpgapaperfinal/FPGAPaper/partitioning.tex
Use roman numerals where lists can be confused with subsections
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4577 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Making a note on the absence of the 90% wires cut result from old paper
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4578 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Updated text for missing 90% wires cut data
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4579 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\begin{enumerate}
  \item Leaving both the packer and the placer unconstrained. This is the base flow that does not use partitioning, as described in Section \ref{cadSection}.
  \item Partitioning the primitive netlist to guide the packer, leaving the placer unconstrained.
  \item Leaving the packer unconstrained, and partitioning the function block (clustered) netlist to guide the placer.
  \item Partitioning the primitive netlist to guide the packer, and, as described above, passing these constraints to the placer.
\end{enumerate}

@@

\subsubsection{Hypergraph to Graph Transformation}\label{sec:hypergraph_to_graph}
We transformed the circuit netlist hypergraph to a graph in the following way:
\begin{enumerate}
\item For each hyperedge of the circuit netlist hypergraph, we generated a graph (the \emph{per-net subgraph}).
\item We combined all of the per-net subgraphs, summing the edge weights for edges appearing in more than one per-net subgraph, to generate the total netlist graph.
\end{enumerate}

@@

\begin{figure}[!htbp]
\centering
\input{wires_cut}
\caption{Impact of partitioning-based CAD flow on routability for a range of architectures.}
\label{fig:wires_cut}
\end{figure}

\subsubsection{Bloating of the Clustered Netlist due to Partitioning Constraints}
The additional constraints on the packer imposed by partitioning may result in a less dense packing. Figure \ref{fig:packing_bloat} compares the number of complex blocks in the partitioning-constrained and unconstrained clustered netlists.

>>>>

\begin{enumerate}[label=(\roman*)]
  \item Leaving both the packer and the placer unconstrained. This is the base flow that does not use partitioning, as described in Section \ref{cadSection}.
  \item Partitioning the primitive netlist to guide the packer, leaving the placer unconstrained.
  \item Leaving the packer unconstrained, and partitioning the function block (clustered) netlist to guide the placer.
  \item Partitioning the primitive netlist to guide the packer, and, as described above, passing these constraints to the placer.
\end{enumerate}

@@

\subsubsection{Hypergraph to Graph Transformation}\label{sec:hypergraph_to_graph}
We transformed the circuit netlist hypergraph to a graph in the following way:
\begin{enumerate}[label=(\roman*)]
\item For each hyperedge of the circuit netlist hypergraph, we generated a graph (the \emph{per-net subgraph}).
\item We combined all of the per-net subgraphs, summing the edge weights for edges appearing in more than one per-net subgraph, to generate the total netlist graph.
\end{enumerate}

@@

\begin{figure}[!htbp]
\centering
\input{wires_cut}
\caption{Impact of partitioning-based CAD flow on routability for a range of architectures.\protect\footnotemark}
\label{fig:wires_cut}
\end{figure}
\footnotetext{The best flow from~\cite{interposer2014} does not provide data at 90\% wires cut.}
\subsubsection{Bloating of the Clustered Netlist due to Partitioning Constraints}
The additional constraints on the packer imposed by partitioning may result in a less dense packing. Figure \ref{fig:packing_bloat} compares the number of complex blocks in the partitioning-constrained and unconstrained clustered netlists.
